\chapter{Conclusion and Thoughts}

\section{Developer Experience}

\begin{enumerate}
    \item It took me about 4 hours to setup a reproducable development environment using 
        VSCode dev containers \cite{containers}
    \item This was tested on Windows and Osx. Allowing me to compile, test and 
        run up a test node. 
    \item I was able to leverage my existing Rust skillset which helped a lot.
    \item The learning curve is steep due to heavy use of the rust type system. 2 Toolchains
        at the same time. And new terminolgy i.e. Parachains etc etc.
    \item There is a tutorial \cite{tutorial}
    \item There is some presence on StackOverflow \cite{overflow}
    \item Incremental build of a contract is just over 1 second.
    \item I raised an issue on github when I couldn't get some code to compile and
     the developers had an answer within 24 hours.
    \item I use rust-analyzer to give me intellisense and to point out compilation issues as
        I type. This worked well but it did give me red marks for compilation errors
        which didn't get flagged on the command line.
\end{enumerate}

\section{Deployment}

I was able to to get a test node up and running. Unfortuantely I couldn't get the 
user interface to connect to my local node. This may be that I'm running the 
from within a docker container.
I was able to use the Restful API to get blockchain information. In time I could get
this working.

\section{Integration Testing and Simulation}


\begin{enumerate}
    \item I have high confidence that I could build a CI/CD pipeline and deploy direct to a testnet.
        This would make the workflow between development and simulation much easier.
    \item Because Edgeware supplies a test network it could be possible
        to run testing without running any of our own infrastructure.
    \item We should consider wether we need to run any blockchain infrastructure
        at all. The production network uses a token, this would mean the 
        operators would pay for RPC calls, but we would not need to run and \
        maintain a network of nodes.
\end{enumerate}


\section{If I Had More Time}

To complete the PoC and cover all the risks of this technolgy I would need to do the following.

\begin{enumerate}
    \item Add functions and structs to manage a negotiation workflow.
    \item Deploy a staging environment including our own nodes.
    \item Get a node and UI running locally so developers can do integration 
    testing on their own machines.
    \item Deploy a minimal UI that can interact with a node.
    \item Deploy the smart contract to the edgeware production network.
\end{enumerate}